---
title: "Manner of Exercise Predict"
author: "Li Gongzuo"
date: "Wednesday, June 21, 2015"
output: html_document
---

##Load and clean the data set
 
1.Load training data
```{r}
setwd("C:/Users/Alan GZ Li/Documents/GitHub/Practical-Machine-Learning")
trainingData <- read.csv("./data/pml-training.csv",na.strings = c("","NA","#DIV/0!"))
trainingData <- trainingData[,-c(1:5)]
```

2.load predict data
```{r}
predictData <- read.csv("./data/pml-testing.csv",na.strings = c("","NA","#DIV/0!"),)
newdata<- rbind(trainingData[1,-155],predictData[,-c(1:5,160)])[-1,]

```

##Built model

1.Setting up training and testing data

```{r}
ind <- sample(2,nrow(trainingData),replace=TRUE,prob=c(0.7,0.3))
training <- trainingData[ind==1,]
testing <- trainingData[ind==2,]
```


2.Apply rpart to bulid the model

```{r results='hide'}
library(party)
```

```{r cache=TRUE}
modFit<-ctree(classe ~ ., data=training)
```

##Cross validation

1.Training data cross validation
```{r}
# predict outcome for train data set
pred.train <- predict(modFit,training)
# logic value for whether or not the model predicted correctly
training$predRight <- pred.train==training$classe
# tabulate results
conf.train<- table(pred.train,training$classe);conf.train
#Compute the expected in sample error
in.sample.error <- length(training[training$predRight==FALSE,]$predRight)/length(training$predRight)
in.sample.error

```

2.Testing data cross validation
```{r}
# predict outcome for test data set
pred.test <- predict(modFit,testing)
# logic value for whether or not the model predicted correctly
testing$predRight <- pred.test==testing$classe
# tabulate results
conf.test <- table(pred.test,testing$classe);conf.test
#Compute the expected out of sample error
out.of.sample.error <- length(testing[testing$predRight==FALSE,]$predRight)/length(testing$predRight)
out.of.sample.error

```

3.Model evaluation and choice

As above, both in sample error and out of sample error are very small. So we can learn that the model fit the data set and will be expected to predict classe well. Besides, will run the model use sample training data sets and predict the classe many time, and then get the most possible results.

##predict 

```{r results='hide'}
# predict outcome for predict data set using the model for many times
library(party)
```

```{r}
results <- matrix(NA,nrow=10,ncol=20)
for (i in 1:nrow(results)) {
        
        # create sample from data with replacement
        inda <- sample(2,nrow(trainingData),replace=TRUE,prob=c(0.7,0.3))
        traininga <- trainingData[inda==1,]
                
        # fit loess function through data (similar to spline)
        modFita<-ctree(classe ~ ., data=traininga)
        
        # predict
        classePred <- as.character(predict(modFita,newdata))
        results[i,] <- classePred
        }
results

#find the most possible classe predict results
fun <- function(x) {
 names(which.max(table(x)))
}

classe.predict <- apply(results,2,fun);classe.predict

```
