---
title: "Manner of Exercise Predict"
author: "Li Gongzuo"
date: "Wednesday, June 17, 2015"
output: html_document
---

##Load and clean the data set
 
1.Load training data
```{r}
setwd("C:/Users/Alan GZ Li/Documents/GitHub/Practical-Machine-Learning")
trainingData <- read.csv("./data/pml-training.csv",na.strings = c("","NA","#DIV/0!"))

```

2.load predict data
```{r}
predictData <- read.csv("./data/pml-testing.csv",na.strings = c("","NA","#DIV/0!"))
#predictData <- read.csv("./data/pml-testing.csv")
newdata<- predictData[,-c(1:5,160)]
        
```

##Built model

1.Setting up training and testing data
```{r}
library(caret)
inTrain <- createDataPartition(y=trainingData$classe,p=0.6, list=FALSE)
training <- trainingData[inTrain,]
testing <- trainingData[-inTrain,]
```

```{r}
ind <- sample(2,nrow(trainingData),replace=TRUE,prob=c(0.6,0.4))
training <- trainingData[ind==1,]
testing <- trainingData[ind==2,]
```

2.Apply rpart to bulid the model

```{r cache=TRUE}
modFit<-train(classe ~ ., data=training, method="rpart")
```

```{r cache=TRUE}
library(party)
modFit<-ctree(classe ~ ., data=training)
```



##Cross validation

1.Training data cross validation
```{r}
# predict outcome for train data set
pred.train <- predict(modFit,training)
# logic value for whether or not the model predicted correctly
training$predRight <- pred.train==training$classe
# tabulate results
conf.train<- table(pred.train,training$classe);conf.train
#Compute the expected in sample error
in.sample.error <- length(training[training$predRight==FALSE,]$predRight)/length(training$predRight)
in.sample.error

```

2.Testing data cross validation
```{r}
# predict outcome for test data set
pred.test <- predict(modFit,testing)
# logic value for whether or not the model predicted correctly
testing$predRight <- pred.test==testing$classe
# tabulate results
conf.test <- table(pred.test,testing$classe);conf.test
#Compute the expected out of sample error
out.of.sample.error <- length(testing[testing$predRight==FALSE,]$predRight)/length(testing$predRight)
out.of.sample.error

```

3.Model evaluation

As above, both in sample error and out of sample error are very small. So we can learn that the model fit the data set and been expected to predict classe well.

##predict 

```{r}
# predict outcome for predict data set using the model
newdata$classePred <- predict(modFit,newdata)
c(predictData$problem_id,newdata$classePred)

```

